---
title: "IMPACTS Medication adherence"
author: "Farah Allouch"
date: "`r format(Sys.time(), ' %B %d, %Y')`"
output: 
  word_document:
    toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE)

rm(list = ls())
options(scipen = 999)

library(tidyverse)
library(gtsummary)
library(flextable)
```

\newpage
```{r}
medAdherence <- haven::read_dta("C:/Users/fallouch/Box/IMPACTS ARMSTRONG/Farah/medicationAdherence/deidRaw/output/medAdherence.dta")

medAdherence <- medAdherence %>% 
  mutate(forget_adh_format = case_when(forget_adh == 0 ~ 1,
                                       forget_adh == 1 ~ 0),
         dnt_adh_format = case_when(dnt_adh == 0 ~ 1,
                                    dnt_adh == 1 ~ 0),
         felt_worse_adh_format = case_when(felt_worse_adh == 0 ~ 1,
                                           felt_worse_adh == 1 ~ 0),
         travel_adh_format = case_when(travel_adh == 0 ~ 1,
                                       travel_adh == 1 ~ 0),
         stop_adh_format = case_when(stop_adh == 0 ~ 1,
                                     stop_adh == 1 ~ 0),
         hassle_adh_format = case_when(hassle_adh == 0 ~ 1,
                                       hassle_adh == 1 ~ 0),
         remember_adh_format = case_when(remember_adh == 1 ~ 1,
                                         remember_adh == 2 ~ 0.75,
                                         remember_adh == 3 ~ 0.5,
                                         remember_adh == 4 ~ 0.25,
                                         remember_adh == 5 ~ 0),
         morisky_score = (forget_adh_format + dnt_adh_format + felt_worse_adh_format + travel_adh_format + yesterday_adh + stop_adh_format + hassle_adh_format + remember_adh_format),
         morisky_score = ifelse(is.na(forget_adh_format) |
                                  is.na(dnt_adh_format) |
                                  is.na(felt_worse_adh_format) |
                                  is.na(travel_adh_format) |
                                  is.na(yesterday_adh) |
                                  is.na(stop_adh_format) |
                                  is.na(hassle_adh_format) |
                                  is.na(remember_adh_format) |
                                  prescribed_adh == 0, NA, morisky_score),
         morisky_score_format = factor(case_when(morisky_score == 8 ~ "High adherence",
                                          between(morisky_score, 6.1, 7.9) ~ "Medium adherence",
                                          morisky_score <= 6 ~ "Low adherence"),
                                       levels = c("High adherence", "Medium adherence", "Low adherence")),
         redcap_event_name = ifelse(redcap_event_name == "bv1sv_arm_1", "bv1", "bv2"),
         not_take_padh_format = case_when(not_take_padh == 1 ~ 4,
                                          not_take_padh == 2 ~ 3,
                                          not_take_padh == 3 ~ 2,
                                          not_take_padh == 4 ~ 1,
                                          not_take_padh == 5 ~ 0),
         cut_back_padh_format = case_when(cut_back_padh == 1 ~ 4,
                                          cut_back_padh == 2 ~ 3,
                                          cut_back_padh == 3 ~ 2,
                                          cut_back_padh == 4 ~ 1,
                                          cut_back_padh == 5 ~ 0),
         pilot_medadh = not_take_padh_format + cut_back_padh_format,
         pilot_medadh = ifelse(is.na(not_take_padh_format) |
                                 is.na(cut_back_padh_format) |
                                 prescr_padh == 0, NA, pilot_medadh),
         uncontrolled_bp_140 = ifelse(sys_avg_bp >= 140 |
                                   dias_avg_bp >= 90, 1, 0))

medAdherence_wide <- pivot_wider(data = medAdherence,
                                 id_cols = record_id,
                                 names_from = redcap_event_name,
                                 values_from = c(age_bdl, sex_bdl, race_bdl, hispanic_bdl, income_bdl,
                                                 sys_avg_bp, dias_avg_bp,
                                                 morisky_score, morisky_score_format,
                                                 pilot_medadh,
                                                 uncontrolled_bp_140))

not_all_na <- function(x) any(!is.na(x))

medAdherence_wide <- medAdherence_wide %>% 
  select(where(not_all_na)) %>% 
  select(-pilot_medadh_bv1) %>%
  filter(!is.na(morisky_score_bv2)) %>% 
  rename(morisky_score = morisky_score_bv2,
         morisky_score_format = morisky_score_format_bv2,
         sbp_bv1 = sys_avg_bp_bv1,
         sbp_bv2 = sys_avg_bp_bv2,
         dbp_bv1 = dias_avg_bp_bv1,
         dbp_bv2 = dias_avg_bp_bv2,
         pilot_medadh = pilot_medadh_bv2) %>% 
  mutate(sbp_bv1_bv2 = (sbp_bv1 + sbp_bv2) / 2,
         dbp_bv1_bv2 = (dbp_bv1 + dbp_bv2) / 2,
         uncontrolled_bp_140_bv1_bv2 = ifelse(uncontrolled_bp_140_bv1 == 1 |
                                                uncontrolled_bp_140_bv2 == 1, 1, 0))
```

# Study population characteristics
```{r}
medAdherence_wide %>% 
  select(-c(record_id,
            sbp_bv1_bv2,
            dbp_bv1_bv2,
            uncontrolled_bp_140_bv1_bv2)) %>% 
  tbl_summary(label = NULL) %>% 
  modify_header(label = "**Variable**") %>% 
  bold_labels()
```

\newpage
# Morisky and BP
## Systolic BP
### BV1 and BV2 average
```{r}
cor.test(medAdherence_wide$sbp_bv1_bv2, medAdherence_wide$morisky_score)

lm(sbp_bv1_bv2 ~ morisky_score_format, data = medAdherence_wide) %>% 
  tbl_regression() %>% 
  modify_caption("Mean systolic BP at BV1 and BV2 on Morisky score") %>% 
  modify_header(label = "**Variable**") %>% 
  bold_labels()

glm(uncontrolled_bp_140_bv1_bv2 ~ morisky_score_format,
    data = medAdherence_wide,
    family = binomial(link = "logit")) %>% 
  tbl_regression(exponentiate = TRUE) %>% 
  modify_caption("Uncontrolled BP (140/90) at BV1 or BV2 on Morisky score") %>% 
  modify_header(label = "**Variable**") %>% 
  bold_labels()

ggplot(aes(x = morisky_score, y = sbp_bv1_bv2), data = medAdherence_wide) +
  geom_point() +
  geom_smooth() +
  xlab("Morisky score") +
  ylab("Mean systolic BP at BV1 and BV2") +
  theme_minimal()
```

\newpage
### BV1 
```{r}
cor.test(medAdherence_wide$sbp_bv1, medAdherence_wide$morisky_score)

lm(sbp_bv1 ~ morisky_score_format, data = medAdherence_wide) %>% 
  tbl_regression() %>% 
  modify_caption("Systolic BP at BV1 on Morisky score") %>% 
  modify_header(label = "**Variable**") %>% 
  bold_labels()

glm(uncontrolled_bp_140_bv1 ~ morisky_score_format,
    data = medAdherence_wide,
    family = binomial(link = "logit")) %>% 
  tbl_regression(exponentiate = TRUE) %>% 
  modify_caption("Uncontrolled BP (140/90) at BV1 on Morisky score") %>% 
  modify_header(label = "**Variable**") %>% 
  bold_labels()

ggplot(aes(x = morisky_score, y = sbp_bv1), data = medAdherence_wide) +
  geom_point() +
  geom_smooth() +
  xlab("Morisky score") +
  ylab("Average systolic BP at BV1") +
  theme_minimal()
```

\newpage
### BV2
```{r}
cor.test(medAdherence_wide$sbp_bv2, medAdherence_wide$morisky_score)

lm(sbp_bv2 ~ morisky_score_format, data = medAdherence_wide) %>% 
  tbl_regression() %>% 
  modify_caption("Systolic BP at BV2 on Morisky score") %>% 
  modify_header(label = "**Variable**") %>% 
  bold_labels()

glm(uncontrolled_bp_140_bv2 ~ morisky_score_format,
    data = medAdherence_wide,
    family = binomial(link = "logit")) %>% 
  tbl_regression(exponentiate = TRUE) %>% 
  modify_caption("Uncontrolled BP (140/90) at BV2 on Morisky score") %>% 
  modify_header(label = "**Variable**") %>% 
  bold_labels()

ggplot(aes(x = morisky_score, y = sbp_bv2), data = medAdherence_wide) +
  geom_point() +
  geom_smooth() +
  xlab("Morisky score") +
  ylab("Average systolic BP at BV2") +
  theme_minimal()
```

\newpage
## Diastolic BP
### BV1 and BV2 average
```{r}
cor.test(medAdherence_wide$dbp_bv1_bv2, medAdherence_wide$morisky_score)

lm(dbp_bv1_bv2 ~ morisky_score_format, data = medAdherence_wide) %>% 
  tbl_regression() %>% 
  modify_caption("Mean systolic BP at BV1 and BV2 on Morisky score") %>% 
  modify_header(label = "**Variable**") %>% 
  bold_labels()

ggplot(aes(x = morisky_score, y = dbp_bv1_bv2), data = medAdherence_wide) +
  geom_point() +
  geom_smooth() +
  xlab("Morisky score") +
  ylab("Mean systolic BP at BV1 and BV2") +
  theme_minimal()
```

\newpage
### BV1
```{r}
cor.test(medAdherence_wide$dbp_bv1, medAdherence_wide$morisky_score)

lm(dbp_bv1 ~ morisky_score_format, data = medAdherence_wide) %>% 
  tbl_regression() %>% 
  modify_caption("Diastolic BP at BV1 on Morisky score") %>% 
  modify_header(label = "**Variable**") %>% 
  bold_labels()

ggplot(aes(x = morisky_score, y = dbp_bv1), data = medAdherence_wide) +
  geom_point() +
  geom_smooth() +
  xlab("Morisky score") +
  ylab("Diastolic systolic BP at BV1") +
  theme_minimal()
```

\newpage
### BV2
```{r}
cor.test(medAdherence_wide$dbp_bv2, medAdherence_wide$morisky_score)

lm(dbp_bv2 ~ morisky_score_format, data = medAdherence_wide) %>% 
  tbl_regression() %>% 
  modify_caption("Diastolic BP at BV2 on Morisky score") %>% 
  modify_header(label = "**Variable**") %>% 
  bold_labels()

ggplot(aes(x = morisky_score, y = dbp_bv2), data = medAdherence_wide) +
  geom_point() +
  geom_smooth() +
  xlab("Morisky score") +
  ylab("Diastolic systolic BP at BV2") +
  theme_minimal()
```

\newpage
# Pilot medication adherence score and Morisky score
```{r}
cor.test(medAdherence_wide$pilot_medadh, medAdherence_wide$morisky_score)

ggplot(aes(x = morisky_score, y = pilot_medadh), data = medAdherence_wide) +
  geom_point() +
  geom_smooth() +
  xlab("Morisky score") +
  ylab("Pilot medication adherence score") +
  theme_minimal()
```

\newpage
# Pilot medication adherence score and BP
## Systolic BP
### BV1 and BV2 average
```{r}
cor.test(medAdherence_wide$sbp_bv1_bv2, medAdherence_wide$pilot_medadh)

glm(uncontrolled_bp_140_bv1_bv2 ~ pilot_medadh,
    data = medAdherence_wide,
    family = binomial(link = "logit")) %>% 
  tbl_regression(exponentiate = TRUE) %>% 
  modify_caption("Uncontrolled BP (140/90) at BV1 or BV2 on Pilot medication adherence score") %>% 
  modify_header(label = "**Variable**") %>% 
  bold_labels()

ggplot(aes(x = pilot_medadh, y = sbp_bv1_bv2), data = medAdherence_wide) +
  geom_point() +
  geom_smooth() +
  xlab("Pilot medication adherence score") +
  ylab("Mean systolic BP at BV1 and BV2") +
  theme_minimal()
```

\newpage
### BV1 
```{r}
cor.test(medAdherence_wide$sbp_bv1, medAdherence_wide$pilot_medadh)

glm(uncontrolled_bp_140_bv1 ~ pilot_medadh,
    data = medAdherence_wide,
    family = binomial(link = "logit")) %>% 
  tbl_regression(exponentiate = TRUE) %>% 
  modify_caption("Uncontrolled BP (140/90) at BV1 on Pilot medication adherence score") %>% 
  modify_header(label = "**Variable**") %>% 
  bold_labels()

ggplot(aes(x = pilot_medadh, y = sbp_bv1), data = medAdherence_wide) +
  geom_point() +
  geom_smooth() +
  xlab("Pilot medication adherence score") +
  ylab("Average systolic BP at BV1") +
  theme_minimal()
```

\newpage
### BV2
```{r}
cor.test(medAdherence_wide$sbp_bv2, medAdherence_wide$pilot_medadh)

glm(uncontrolled_bp_140_bv2 ~ pilot_medadh,
    data = medAdherence_wide,
    family = binomial(link = "logit")) %>% 
  tbl_regression(exponentiate = TRUE) %>% 
  modify_caption("Uncontrolled BP (140/90) at BV2 on Pilot medication adherence score") %>% 
  modify_header(label = "**Variable**") %>% 
  bold_labels()

ggplot(aes(x = pilot_medadh, y = sbp_bv2), data = medAdherence_wide) +
  geom_point() +
  geom_smooth() +
  xlab("Pilot medication adherence score") +
  ylab("Average systolic BP at BV2") +
  theme_minimal()
```

\newpage
## Diastolic BP
### BV1 and BV2 average
```{r}
cor.test(medAdherence_wide$dbp_bv1_bv2, medAdherence_wide$pilot_medadh)

ggplot(aes(x = pilot_medadh, y = dbp_bv1_bv2), data = medAdherence_wide) +
  geom_point() +
  geom_smooth() +
  xlab("Pilot medication adherence score") +
  ylab("Mean systolic BP at BV1 and BV2") +
  theme_minimal()
```

\newpage
### BV1
```{r}
cor.test(medAdherence_wide$dbp_bv1, medAdherence_wide$pilot_medadh)

ggplot(aes(x = pilot_medadh, y = dbp_bv1), data = medAdherence_wide) +
  geom_point() +
  geom_smooth() +
  xlab("Pilot medication adherence score") +
  ylab("Diastolic systolic BP at BV1") +
  theme_minimal()
```

\newpage
### BV2
```{r}
cor.test(medAdherence_wide$dbp_bv2, medAdherence_wide$pilot_medadh)

ggplot(aes(x = pilot_medadh, y = dbp_bv2), data = medAdherence_wide) +
  geom_point() +
  geom_smooth() +
  xlab("Pilot medication adherence score") +
  ylab("Diastolic systolic BP at BV2") +
  theme_minimal()
```