---
title: "IMPACTS Medication adherence by sex"
author: "Farah Allouch"
date: "`r format(Sys.time(), ' %B %d, %Y')`"
output: 
  word_document:
    toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE)

rm(list = ls())
options(scipen = 999)

library(tidyverse)
library(gtsummary)
library(flextable)

load("../output/medAdherence_wide.Rdata")

medAdherence_wide_Male <- medAdherence_wide %>% 
  filter(sex_bdl_bv2 == 1)

medAdherence_wide_Female <- medAdherence_wide %>% 
  filter(sex_bdl_bv2 == 2)
```

\newpage
# Study population characteristics
```{r table_one}
medAdherence_wide %>% 
  select(-c(record_id,
            sbp_bv1_bv2,
            dbp_bv1_bv2,
            pilot_medadh_format_7_reg_bv2,
            pilot_medadh_format_8_reg_bv2)) %>% 
  filter(sex_bdl_bv2 == 1 |
           sex_bdl_bv2 == 2) %>% 
  tbl_summary(by = sex_bdl_bv2,
              label = NULL) %>% 
  modify_header(label = "**Variable**") %>% 
  bold_labels()
```

\newpage
# Morisky and BP
## Systolic BP
### BV1 and BV2 average
**Male**
```{r morisky-sbp-Male}
cor.test(medAdherence_wide_Male$sbp_bv1_bv2, medAdherence_wide_Male$morisky_score)

lm(sbp_bv1_bv2 ~ morisky_score_format, data = medAdherence_wide_Male) %>% 
  tbl_regression() %>% 
  modify_caption("Mean systolic BP at BV1 and BV2 on Morisky score") %>% 
  modify_header(label = "**Variable**") %>% 
  bold_labels()

glm(uncontrolled_bp_140_6BP ~ morisky_score_format,
    data = medAdherence_wide_Male,
    family = binomial(link = "logit")) %>% 
  tbl_regression(exponentiate = TRUE) %>% 
  modify_caption("Uncontrolled BP (140/90) at BV1/BV2 average on Morisky score") %>% 
  modify_header(label = "**Variable**") %>% 
  bold_labels()

ggplot(aes(x = morisky_score, y = sbp_bv1_bv2), data = medAdherence_wide_Male) +
  geom_point() +
  geom_smooth() +
  xlab("Morisky score") +
  ylab("Mean systolic BP at BV1 and BV2") +
  theme_minimal()
```

**Female**
```{r morisky-sbp-Female}
cor.test(medAdherence_wide_Female$sbp_bv1_bv2, medAdherence_wide_Female$morisky_score)

lm(sbp_bv1_bv2 ~ morisky_score_format, data = medAdherence_wide_Female) %>% 
  tbl_regression() %>% 
  modify_caption("Mean systolic BP at BV1 and BV2 on Morisky score") %>% 
  modify_header(label = "**Variable**") %>% 
  bold_labels()

glm(uncontrolled_bp_140_6BP ~ morisky_score_format,
    data = medAdherence_wide_Female,
    family = binomial(link = "logit")) %>% 
  tbl_regression(exponentiate = TRUE) %>% 
  modify_caption("Uncontrolled BP (140/90) at BV1/BV2 average on Morisky score") %>% 
  modify_header(label = "**Variable**") %>% 
  bold_labels()

ggplot(aes(x = morisky_score, y = sbp_bv1_bv2), data = medAdherence_wide_Female) +
  geom_point() +
  geom_smooth() +
  xlab("Morisky score") +
  ylab("Mean systolic BP at BV1 and BV2") +
  theme_minimal()
```

\newpage
### BV1 
**Male**
```{r morisky-sbp-Male-bv1}
cor.test(medAdherence_wide_Male$sbp_bv1, medAdherence_wide_Male$morisky_score)

lm(sbp_bv1 ~ morisky_score_format, data = medAdherence_wide_Male) %>% 
  tbl_regression() %>% 
  modify_caption("Systolic BP at BV1 on Morisky score") %>% 
  modify_header(label = "**Variable**") %>% 
  bold_labels()

glm(uncontrolled_bp_140_BV1 ~ morisky_score_format,
    data = medAdherence_wide_Male,
    family = binomial(link = "logit")) %>% 
  tbl_regression(exponentiate = TRUE) %>% 
  modify_caption("Uncontrolled BP (140/90) at BV1 on Morisky score") %>% 
  modify_header(label = "**Variable**") %>% 
  bold_labels()

ggplot(aes(x = morisky_score, y = sbp_bv1), data = medAdherence_wide_Male) +
  geom_point() +
  geom_smooth() +
  xlab("Morisky score") +
  ylab("Average systolic BP at BV1") +
  theme_minimal()
```

**Female**
```{r morisky-sbp-Female-bv1}
cor.test(medAdherence_wide_Female$sbp_bv1, medAdherence_wide_Female$morisky_score)

lm(sbp_bv1 ~ morisky_score_format, data = medAdherence_wide_Female) %>% 
  tbl_regression() %>% 
  modify_caption("Systolic BP at BV1 on Morisky score") %>% 
  modify_header(label = "**Variable**") %>% 
  bold_labels()

glm(uncontrolled_bp_140_BV1 ~ morisky_score_format,
    data = medAdherence_wide_Female,
    family = binomial(link = "logit")) %>% 
  tbl_regression(exponentiate = TRUE) %>% 
  modify_caption("Uncontrolled BP (140/90) at BV1 on Morisky score") %>% 
  modify_header(label = "**Variable**") %>% 
  bold_labels()

ggplot(aes(x = morisky_score, y = sbp_bv1), data = medAdherence_wide_Female) +
  geom_point() +
  geom_smooth() +
  xlab("Morisky score") +
  ylab("Average systolic BP at BV1") +
  theme_minimal()
```

\newpage
## Diastolic BP
### BV1 and BV2 average
**Male**
```{r morisky-dbp-Male}
cor.test(medAdherence_wide_Male$dbp_bv1_bv2, medAdherence_wide_Male$morisky_score)

lm(dbp_bv1_bv2 ~ morisky_score_format, data = medAdherence_wide_Male) %>% 
  tbl_regression() %>% 
  modify_caption("Mean systolic BP at BV1 and BV2 on Morisky score") %>% 
  modify_header(label = "**Variable**") %>% 
  bold_labels()

ggplot(aes(x = morisky_score, y = dbp_bv1_bv2), data = medAdherence_wide_Male) +
  geom_point() +
  geom_smooth() +
  xlab("Morisky score") +
  ylab("Mean systolic BP at BV1 and BV2") +
  theme_minimal()
```

**Female**
```{r morisky-dbp-Female}
cor.test(medAdherence_wide_Female$dbp_bv1_bv2, medAdherence_wide_Female$morisky_score)

lm(dbp_bv1_bv2 ~ morisky_score_format, data = medAdherence_wide_Female) %>% 
  tbl_regression() %>% 
  modify_caption("Mean systolic BP at BV1 and BV2 on Morisky score") %>% 
  modify_header(label = "**Variable**") %>% 
  bold_labels()

ggplot(aes(x = morisky_score, y = dbp_bv1_bv2), data = medAdherence_wide_Female) +
  geom_point() +
  geom_smooth() +
  xlab("Morisky score") +
  ylab("Mean systolic BP at BV1 and BV2") +
  theme_minimal()
```

\newpage
### BV1
**Male**
```{r morisky-dbp-Male-bv1}
cor.test(medAdherence_wide_Male$dbp_bv1, medAdherence_wide_Male$morisky_score)

lm(dbp_bv1 ~ morisky_score_format, data = medAdherence_wide_Male) %>% 
  tbl_regression() %>% 
  modify_caption("Diastolic BP at BV1 on Morisky score") %>% 
  modify_header(label = "**Variable**") %>% 
  bold_labels()

ggplot(aes(x = morisky_score, y = dbp_bv1), data = medAdherence_wide_Male) +
  geom_point() +
  geom_smooth() +
  xlab("Morisky score") +
  ylab("Diastolic systolic BP at BV1") +
  theme_minimal()
```

**Female**
```{r morisky-dbp-Female-bv1}
cor.test(medAdherence_wide_Female$dbp_bv1, medAdherence_wide_Female$morisky_score)

lm(dbp_bv1 ~ morisky_score_format, data = medAdherence_wide_Female) %>% 
  tbl_regression() %>% 
  modify_caption("Diastolic BP at BV1 on Morisky score") %>% 
  modify_header(label = "**Variable**") %>% 
  bold_labels()

ggplot(aes(x = morisky_score, y = dbp_bv1), data = medAdherence_wide_Female) +
  geom_point() +
  geom_smooth() +
  xlab("Morisky score") +
  ylab("Diastolic systolic BP at BV1") +
  theme_minimal()
```

\newpage
# Pilot medication adherence score and Morisky score
**Male**
```{r}
cor.test(medAdherence_wide_Male$pilot_medadh, medAdherence_wide_Male$morisky_score)
```

**Female**
```{r}
cor.test(medAdherence_wide_Female$pilot_medadh, medAdherence_wide_Female$morisky_score)
```

**Male**
``` {r}
medAdherence_wide_Male <- medAdherence_wide_Male %>% 
  mutate(morisky_score_format = factor(morisky_score_format,
                                       levels = c("Low adherence", "Medium adherence", "High adherence")))

glm(pilot_medadh_format_8_reg_bv2 ~ morisky_score_format,
    data = medAdherence_wide_Male,
    family = binomial(link = "logit")) %>% 
  tbl_regression(exponentiate = TRUE) %>% 
  modify_caption("Pilot medication adherence scale (==8) on Morisky score") %>% 
  modify_header(label = "**Variable**") %>% 
  bold_labels()

ggplot(aes(x = morisky_score, y = pilot_medadh), data = medAdherence_wide_Male) +
  geom_point() +
  geom_smooth() +
  xlab("Morisky score") +
  ylab("Pilot medication adherence score") +
  theme_minimal()
```

**Female**
``` {r}
medAdherence_wide_Female <- medAdherence_wide_Female %>% 
  mutate(morisky_score_format = factor(morisky_score_format,
                                       levels = c("Low adherence", "Medium adherence", "High adherence")))

glm(pilot_medadh_format_8_reg_bv2 ~ morisky_score_format,
    data = medAdherence_wide_Female,
    family = binomial(link = "logit")) %>% 
  tbl_regression(exponentiate = TRUE) %>% 
  modify_caption("Pilot medication adherence scale (==8) on Morisky score") %>% 
  modify_header(label = "**Variable**") %>% 
  bold_labels()

ggplot(aes(x = morisky_score, y = pilot_medadh), data = medAdherence_wide_Female) +
  geom_point() +
  geom_smooth() +
  xlab("Morisky score") +
  ylab("Pilot medication adherence score") +
  theme_minimal()
```

\newpage
# Pilot medication adherence score and BP
## Systolic BP
### BV1 and BV2 average
**Male**
```{r}
cor.test(medAdherence_wide_Male$sbp_bv1_bv2, medAdherence_wide_Male$pilot_medadh)

lm(sbp_bv1_bv2 ~ pilot_medadh_format_8_bv2, data = medAdherence_wide_Male) %>% 
  tbl_regression() %>% 
  modify_caption("Systolic BP at BV1/BV2 average on Pilot medication adherence score (==8)") %>% 
  modify_header(label = "**Variable**") %>% 
  bold_labels()

glm(uncontrolled_bp_140_6BP ~ pilot_medadh_format_8_bv2,
    data = medAdherence_wide_Male,
    family = binomial(link = "logit")) %>% 
  tbl_regression(exponentiate = TRUE) %>% 
  modify_caption("Uncontrolled BP (140/90) at BV1/BV2 average on Pilot medication adherence score (==8)") %>% 
  modify_header(label = "**Variable**") %>% 
  bold_labels()

ggplot(aes(x = pilot_medadh, y = sbp_bv1_bv2), data = medAdherence_wide_Male) +
  geom_point() +
  geom_smooth() +
  xlab("Pilot medication adherence score") +
  ylab("Mean systolic BP at BV1 and BV2") +
  theme_minimal()
```

**Female**
```{r}
cor.test(medAdherence_wide_Female$sbp_bv1_bv2, medAdherence_wide_Female$pilot_medadh)

lm(sbp_bv1_bv2 ~ pilot_medadh_format_8_bv2, data = medAdherence_wide_Female) %>% 
  tbl_regression() %>% 
  modify_caption("Systolic BP at BV1/BV2 average on Pilot medication adherence score (==8)") %>% 
  modify_header(label = "**Variable**") %>% 
  bold_labels()

glm(uncontrolled_bp_140_6BP ~ pilot_medadh_format_8_bv2,
    data = medAdherence_wide_Female,
    family = binomial(link = "logit")) %>% 
  tbl_regression(exponentiate = TRUE) %>% 
  modify_caption("Uncontrolled BP (140/90) at BV1/BV2 average on Pilot medication adherence score (==8)") %>% 
  modify_header(label = "**Variable**") %>% 
  bold_labels()

ggplot(aes(x = pilot_medadh, y = sbp_bv1_bv2), data = medAdherence_wide_Female) +
  geom_point() +
  geom_smooth() +
  xlab("Pilot medication adherence score") +
  ylab("Mean systolic BP at BV1 and BV2") +
  theme_minimal()
```

\newpage
### BV1 
**Male**
```{r}
cor.test(medAdherence_wide_Male$sbp_bv1, medAdherence_wide_Male$pilot_medadh)

lm(sbp_bv1 ~ pilot_medadh_format_8_bv2, data = medAdherence_wide_Male) %>% 
  tbl_regression() %>% 
  modify_caption("Systolic BP at BV1 on Pilot medication adherence score (==8)") %>% 
  modify_header(label = "**Variable**") %>% 
  bold_labels()

glm(uncontrolled_bp_140_BV1 ~ pilot_medadh_format_8_bv2,
    data = medAdherence_wide_Male,
    family = binomial(link = "logit")) %>% 
  tbl_regression(exponentiate = TRUE) %>% 
  modify_caption("Uncontrolled BP (140/90) at BV1 on Pilot medication adherence score (==8)") %>% 
  modify_header(label = "**Variable**") %>% 
  bold_labels()

ggplot(aes(x = pilot_medadh, y = sbp_bv1), data = medAdherence_wide_Male) +
  geom_point() +
  geom_smooth() +
  xlab("Pilot medication adherence score") +
  ylab("Average systolic BP at BV1") +
  theme_minimal()
```

**Female**
```{r}
cor.test(medAdherence_wide_Female$sbp_bv1, medAdherence_wide_Female$pilot_medadh)

lm(sbp_bv1 ~ pilot_medadh_format_8_bv2, data = medAdherence_wide_Female) %>% 
  tbl_regression() %>% 
  modify_caption("Systolic BP at BV1 on Pilot medication adherence score (==8)") %>% 
  modify_header(label = "**Variable**") %>% 
  bold_labels()

glm(uncontrolled_bp_140_BV1 ~ pilot_medadh_format_8_bv2,
    data = medAdherence_wide_Female,
    family = binomial(link = "logit")) %>% 
  tbl_regression(exponentiate = TRUE) %>% 
  modify_caption("Uncontrolled BP (140/90) at BV1 on Pilot medication adherence score (==8)") %>% 
  modify_header(label = "**Variable**") %>% 
  bold_labels()

ggplot(aes(x = pilot_medadh, y = sbp_bv1), data = medAdherence_wide_Female) +
  geom_point() +
  geom_smooth() +
  xlab("Pilot medication adherence score") +
  ylab("Average systolic BP at BV1") +
  theme_minimal()
```

\newpage
## Diastolic BP
### BV1 and BV2 average
**Male**
```{r}
cor.test(medAdherence_wide_Male$dbp_bv1_bv2, medAdherence_wide_Male$pilot_medadh)

lm(dbp_bv1_bv2 ~ pilot_medadh_format_8_bv2, data = medAdherence_wide_Male) %>% 
  tbl_regression() %>% 
  modify_caption("Diastolic BP at BV1/BV2 average on Pilot medication adherence score (==8)") %>% 
  modify_header(label = "**Variable**") %>% 
  bold_labels()

ggplot(aes(x = pilot_medadh, y = dbp_bv1_bv2), data = medAdherence_wide_Male) +
  geom_point() +
  geom_smooth() +
  xlab("Pilot medication adherence score") +
  ylab("Mean systolic BP at BV1 and BV2") +
  theme_minimal()
```

**Female**
```{r}
cor.test(medAdherence_wide_Female$dbp_bv1_bv2, medAdherence_wide_Female$pilot_medadh)

lm(dbp_bv1_bv2 ~ pilot_medadh_format_8_bv2, data = medAdherence_wide_Female) %>% 
  tbl_regression() %>% 
  modify_caption("Diastolic BP at BV1/BV2 average on Pilot medication adherence score (==8)") %>% 
  modify_header(label = "**Variable**") %>% 
  bold_labels()

ggplot(aes(x = pilot_medadh, y = dbp_bv1_bv2), data = medAdherence_wide_Female) +
  geom_point() +
  geom_smooth() +
  xlab("Pilot medication adherence score") +
  ylab("Mean systolic BP at BV1 and BV2") +
  theme_minimal()
```

\newpage
### BV1
**Male**
```{r}
cor.test(medAdherence_wide_Male$dbp_bv1, medAdherence_wide_Male$pilot_medadh)

lm(dbp_bv1 ~ pilot_medadh_format_8_bv2, data = medAdherence_wide_Male) %>% 
  tbl_regression() %>% 
  modify_caption("Diastolic BP at BV1 on Pilot medication adherence score (==8)") %>% 
  modify_header(label = "**Variable**") %>% 
  bold_labels()

ggplot(aes(x = pilot_medadh, y = dbp_bv1), data = medAdherence_wide_Male) +
  geom_point() +
  geom_smooth() +
  xlab("Pilot medication adherence score") +
  ylab("Diastolic systolic BP at BV1") +
  theme_minimal()
```

**Female**
```{r}
cor.test(medAdherence_wide_Female$dbp_bv1, medAdherence_wide_Female$pilot_medadh)

lm(dbp_bv1 ~ pilot_medadh_format_8_bv2, data = medAdherence_wide_Female) %>% 
  tbl_regression() %>% 
  modify_caption("Diastolic BP at BV1 on Pilot medication adherence score (==8)") %>% 
  modify_header(label = "**Variable**") %>% 
  bold_labels()

ggplot(aes(x = pilot_medadh, y = dbp_bv1), data = medAdherence_wide_Female) +
  geom_point() +
  geom_smooth() +
  xlab("Pilot medication adherence score") +
  ylab("Diastolic systolic BP at BV1") +
  theme_minimal()
```